3D Magnetic modelling of ellipsoidal bodies

### 2017-02-08 manuscript/manuscript.tex
modify the end of the introduction, correct elements n-tilde-dagger and put some alerts

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $U$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any body uniformly magnetized in a given direction.
By presuming that this uniform magnetization is due to
induction, he postulated that the resulting magnetic
field (intensity) at all points within the body must
also be uniform and parallel to the magnetization.
As a consequence, the gravitational potential 
$U$ at points within the body must be a quadratic 
function of the spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
postulate that ellipsoids are the only finite bodies 
having a gravitational potential which satisfies this 
property and hence can be uniformly magnetized 
in the presence of a uniform magnetic field.

This property can be extended to other bodies
whose shape derives from an ellipsoid 
(e.g., spheres, elliptic cylinders), however all the
remaining non-ellipsoidal bodies cannot be
uniformly magnetized in the presence of a uniform
inducing field.

@@

It is well-known by that the self-demagnetization can 
be neglected if the body has a susceptibility lower 
than 0.1 SI \citep{austin2014, clark2014, clark1986, 
emerson1985, eskola1980, guo1998, guo2001, purss2005,
hillan2013}.

However, neglecting the self-demagnetization in
geological bodies with high susceptibilities (> 0.1 SI) 
may strongly mislead the results obtained from
magnetic methods.

\citet{farrar1979} demonstrated the importance of the
ellipsoidal model in taking into account the 
self-demagnetization and determining reliable 
drilling directions on the Tennant Creek field, 
Australia.

Posteriorly, \citet{hoschke1991} also showed how the
ellipsoidal model proved to be highly successful in
locating and defining ironstone bodies in the
Tennant Creek field.

\citet{clark2000} provides a good discussion about the
influence of the self-demagnetization in magnetic
interpretation of the Osborne copper-gold deposit, 
Australia. This deposit is hosted by ironstone 
bodies that have very high susceptibility.
According to \citet{clark2000}, neglecting the effects 
of self-demagnetisation led errors of $\approx 55^{\circ}$
in the interpreted dip.

Based on magnetic modelling and rock property 
measurements, \citet{austin2014} showed that,
contrary to previous interpretations, the magnetization
of the Candelaria iron oxide copper-gold deposit, 
Chile, is not dominated by the induced component.
Rather, the deposit has a relatively weak remanent 
magnetization and is strongly affected by 
self-demagnetization.

These examples show the practical importance of
self-demagnetization for the correct interpretation
of magnetic data produced by geological bodies having
high susceptibilities.

These examples also show the importance of the ellipsoidal
model in producing trustworthy geological models of orebodies,
which may save significant cost associated with drilling.

%The ellipsoidal model ability in analytically
%incorporating the self-demagnetization...
%FALAR DA APLICACAO DIDATICA

%Apesar da grande aplicabilidade do modelo elipsoidal 
%na geofísica, apenas alguns softwares proprietários 
%possuem sua implementação. Neste sentido, este trabalho 
%tem a finalidade de disponibilizar uma ferramenta de 
%código aberto, que poderá ser utilizada livremente 
%por toda a comunidade geofísica. 
%exemplo1:
%Isostasy is one of the oldest and most widely applied
%concepts in the geosciences, but the geoscientific community
%lacks a coherent, easy-to-use tool to simulate flexure
%of a realistic (i.e., laterally heterogeneous) lithosphere under
%an arbitrary set of surface loads. Such a model is needed for
%studies of mountain building, sedimentary basin formation,
%glaciation, sea-level change, and other tectonic, geodynamic,
%and surface processes.
%exemplo2:
%In spite of these efforts,
%the community currently lacks a robust, easy-to-use,
%generalized tool for flexural isostatic solutions that can be
%used by modelers and data-driven scientists alike.

@@

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. 
In general, the susceptibility tensor $\mathbf{K}$ is represented as
follows:
\begin{equation}
\mathbf{K} = \mathbf{U}
\left[ \begin{array}{ccc}
k_{1} & 0 & 0 \\
0 & k_{2} & 0 \\
0 & 0 & k_{3} 
\end{array} \right] \mathbf{U}^{\top} \: ,
\label{eq:K}
\end{equation}
where $k_{1} > k_{2} > k_{3}$ are the 
\textit{principal susceptibilities} and $\mathbf{U}$ is
an orthogonal matrix whose columns $\mathbf{u}_{i}$,
$i = 1, 2, 3$, are unit vectors called 
\textit{principal directions} \citep{hrouda1982}.
For the particular case in which the principal directions 
coincide with the ellipsoid axes, $\mathbf{U} = \mathbf{V}$
where $\mathbf{V}$ is defined by Eq. \ref{eq:V_triaxial_prolate} 
or \ref{eq:V_oblate}), depending on the ellipsoid type.

@@

To continue our description of the magnetic modelling of 
ellipsoidal bodies, it is convenient to perform two 
important coordinate transformations. 
The first one transforms the scalar function 
$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
main coordinate system into a new scalar function 
$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
local coordinate system.
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
lowes1974,  peake1953, chang1961, clark1986, tejedor1995, sttraton2007}.

@@

@@

For triaxial ellipsoids (e.g., $a > b > c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:n-tilde-dagger-11-triaxial}
\end{equation}
\begin{equation}
\tilde{n}^{\dagger}_{22} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
- \frac{c^{2}}{b^{2} - c^{2}}
\label{eq:n-tilde-dagger-22-triaxial}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{33} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
\frac{b^{2}}{b^{2} - c^{2}} \: ,
\label{eq:n-tilde-dagger-33-triaxial}
\end{equation}
where
\begin{equation}
F(\kappa, \phi) = 
\int^{\phi}_{0} 
\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
d\psi \: ,
\label{eq:F-kappa-phi}
\end{equation}
and
\begin{equation}
E(\kappa, \phi) = 
\int^{\phi}_{0} 
\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
d\psi \: ,
\label{eq:E-kappa-phi}
\end{equation}
with $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$ and
$\cos \phi = c/a$.
The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
called Legendre's normal elliptic integrals of the first and 
second kind, respectivelly. \citet{stoner1945} presented a 
detailed deduction of the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
formulas, but without any proof.

@@

For prolate ellipsoids (e.g., $a > b = c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
- 1 \right\rbrace
\label{eq:n-tilde-dagger-11-prolate}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
\label{eq:n-tilde-dagger-22-prolate}
\end{equation}
where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
which uses the $\tilde{n}^{\dagger}_{11}$ defined in 
Eq. \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
The detailed deduction of the demagnetizing factors 
$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
can be found, for example, in \citet{stoner1945}. 
These formulas were posteriorly 
presented by \citet{emerson1985}, but without any mathematical proof.

@@

For oblate ellipsoids (e.g., $a < b = c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = 
\frac{1}{1 - m^{2}} \left[
1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
\right] \: ,
\label{eq:n-tilde-dagger-11-oblate}
\end{equation}
where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
are calculated according to Eq.
\ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
defined in Equation \ref{eq:n-tilde-dagger-11-oblate}, 
and $m = a/b$.
The detailed deduction of these demagnetizing factors 
can be found, for example, in \citet{stoner1945}. These formulas can also be found
in \citet{emerson1985}, but without any mathematical proof.
The only difference, however, is that \citet{emerson1985} replaced
the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
the trigonometric identity 
$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.

@@

For triaxial ellipsoids (e.g., $a > b > c$), the functions
$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows
\citep{clark1986}:

\begin{equation}
g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:g1-triaxial}
\end{equation}
\begin{equation}
g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
\left[ E\left(\kappa, \phi \right) 
- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
F\left(\kappa, \phi \right) 
- \frac{\kappa^{2} \sin\phi \, \cos\phi}
{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
\right]
\label{eq:g2-triaxial}
\end{equation}
and
\begin{equation}
g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
{\cos\phi}  - E\left(\kappa, \phi \right) \right]
\: ,
\label{eq:g3-triaxial}
\end{equation}
where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi},
but with 
$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.

FALAR DO \citet{tejedor1995}

@@

For prolate (e.g., $a > b = c$) ellipsoids, the functions
$g_{i}$ (Eq. \ref{eq:gi}) are given by
\citep{emerson1985}:

\begin{equation}
g_{1} =  \frac{2}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right] -
\left( \frac{a^{2} - b^{2}}{a^{2} + \lambda} \right)^{\frac{1}{2}}
\right\rbrace
\label{eq:g1-prolate}
\end{equation}
and
\begin{equation}
g_{2} =  \frac{1}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\frac{\left[ \left( a^{2} - b^{2} \right)
             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
     {b^{2} + \lambda} -
\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right]
\right\rbrace \: ,
\label{eq:g2-prolate}
\end{equation}
where $g_{3} = g_{2}$.

@@

For oblate (e.g., $a < b = c$) ellipsoids, the functions
$g_{i}$ (Eq. \ref{eq:gi}) are given by
\citep{emerson1985}:

\begin{equation}
g_{1} =  \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} -
\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right]
\right\rbrace
\label{eq:g1-oblate}
\end{equation}
and
\begin{equation}
g_{2} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right] -
\frac{\left[ \left( b^{2} - a^{2} \right)
             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
     {b^{2} + \lambda}
\right\rbrace \: ,
\label{eq:g2-oblate}
\end{equation}
where $g_{3} = g_{2}$.

>>>>

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $U$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any body uniformly magnetized in a given direction.
By presuming that this uniform magnetization is due to
induction, he postulated that the resulting magnetic
field (intensity) at all points within the body must
also be uniform and parallel to the magnetization.
As a consequence, the gravitational potential 
$U$ at points within the body must be a quadratic 
function of the spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
postulate that ellipsoids are the only finite bodies 
having a gravitational potential which satisfies this 
property and hence can be uniformly magnetized 
in the presence of a uniform magnetic field.
This property can be extended to other bodies
defined as limiting cases of an ellipsoid
(e.g., spheres, elliptic cylinders), however all the
remaining non-ellipsoidal bodies cannot be
uniformly magnetized in the presence of a uniform
inducing field.

@@

It is well-known by that the self-demagnetization can 
be neglected if the body has a susceptibility lower 
than 0.1 SI \citep{austin2014, clark2014, clark1986, 
emerson1985, eskola1980, guo1998, guo2001, purss2005,
hillan2013}.
However, neglecting the self-demagnetization in
geological bodies with high susceptibilities (> 0.1 SI) 
may strongly mislead the interpretation obtained from
magnetic methods.
\citet{farrar1979} demonstrated the importance of the
ellipsoidal model in taking into account the 
self-demagnetization and determining reliable 
drilling directions on the Tennant Creek field, 
Australia.
Posteriorly, \citet{hoschke1991} also showed how the
ellipsoidal model proved to be highly successful in
locating and defining ironstone bodies in the
Tennant Creek field.
\citet{clark2000} provides a good discussion about the
influence of the self-demagnetization in magnetic
interpretation of the Osborne copper-gold deposit, 
Australia. This deposit is hosted by ironstone 
bodies that have very high susceptibility.
According to \citet{clark2000}, neglecting the effects 
of self-demagnetisation led errors of $\approx 55^{\circ}$
in the interpreted dip. 
Recently, \citet{austin2014} used magnetic modelling 
and rock property measurements to show that,
contrary to previous interpretations, the magnetization
of the Candelaria iron oxide copper-gold deposit, 
Chile, is not dominated by the induced component.
Rather, the deposit has a relatively weak remanent 
magnetization and is strongly affected by 
self-demagnetization.
These examples show the importance of the ellipsoidal
model in producing trustworthy geological models of
high-susceptibility orebodies, which may save significant 
cost associated with drilling.

As we can see, a vast literature about the magnetic
modelling of ellipsoidal bodies was developed in which 
are to be found the names of many brilliant researchers.
Nevertheless, interest in this subject has not yet died
out, as is evidenced by the list of modern papers in this
field.
Besides, the geoscientific community lacks an easy-to-use 
tool to simulate the magnetic field produced by uniformly 
magnetized ellipsoids.
Such a tool could prove to be useful either for teaching
and researching geophysics.

To fill this gap, we provide here a set of routines to 
model the magnetic field produced by ellipsoids.
The routines are written in Python language as part of
the Fatiando a Terra \citep{uieda2013}, which is an 
open-source library for modelling and inversion in geophysics.
We attempt to use the best practices of continuous 
integration, documentation, unit-testing, and version-control
for the purpose of providing a reliable and easy-to-use
code.
It is hoped that the presentation of the theoretical and
practical aspects given here will be found useful to the
wide community of geoscientists.

@@

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. 
In general, the susceptibility tensor $\mathbf{K}$ is represented,
in the main coordinate system, as follows:
\begin{equation}
\mathbf{K} = \mathbf{U}
\left[ \begin{array}{ccc}
k_{1} & 0 & 0 \\
0 & k_{2} & 0 \\
0 & 0 & k_{3} 
\end{array} \right] \mathbf{U}^{\top} \: ,
\label{eq:K}
\end{equation}
where $k_{1} > k_{2} > k_{3}$ are the 
\textit{principal susceptibilities} and $\mathbf{U}$ is
an orthogonal matrix whose columns $\mathbf{u}_{i}$,
$i = 1, 2, 3$, are unit vectors called 
\textit{principal directions} \citep{hrouda1982}.
For the particular case in which the principal directions 
coincide with the ellipsoid axes, the matrix $\mathbf{U}$ is
equal to the matrix $\mathbf{V}$ (Eqs. \ref{eq:V_triaxial_prolate}
and \ref{eq:V_oblate}), depending on the ellipsoid type.

@@

To continue our description of the magnetic modelling of 
ellipsoidal bodies, it is convenient to perform two 
important coordinate transformations. 
The first one transforms the scalar function 
$f(\mathbf{r})$ (Eq. \ref{eq:f}) from the 
main coordinate system into a new scalar function 
$\tilde{f}(\tilde{\mathbf{r}})$ referred to the
local coordinate system.
The function $\tilde{f}(\tilde{\mathbf{r}})$ was first 
presented by \citet{dirichlet1839} to describe the gravitational potential
produced by homogeneous ellipsoids.
Posteriorly, several authors also deduced and used this function
for describing the magnetic and gravitational fields produced
by triaxial, prolate, and oblate ellipsoids  
\citep{maxwell1873, thomson1879, dubois1896, 
peirce1902, webster1904, kellogg1929, stoner1945, osborn1945,
macmillan1958, lowes1974,  peake1953, chang1961, clark1986, 
tejedor1995, sttraton2007}.

@@

FALAR QUE ESTA EQUACAO REPRESENTA O CASO HOMOGENEO ANISOTROPICO. 
FALAR QUE A MAIORIA DOS TRABALHOS DISCUTE O CASO HOMOGENEO ISOTROPICO
(CITAR TRABALHOS)
O CASO ANISOTROPICO FOI APRESENTADO PELA PRIMEIRA VEZ POR \citet{soliverez1981} and
posteriorly by \citet{emerson1985} and \citet{clark1986} (CHECAR).

FALAR DO CASO PARTICULAR EM QUE A SUSCETIBILIDADE EH MUITO FRACA E
A REMANENCIA EH NULA. NESTE CASO, A MAGNETIZACAO EH A FORMULA CLASSICA
DE MAGNETIZACAO INDUZIDA ENCONTRADA NOS LIVROS.

FALAR TAMBEM SOBRE O CASO ISOTROPICO E CITAR O TRABALHO DO GUO 2001.
USAR OS TERMOS INTRINSIC E EFFECTIVE MAGNETIZATIONS.

@@

For triaxial ellipsoids (e.g., $a > b > c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:n-tilde-dagger-11-triaxial}
\end{equation}
\begin{equation}
\tilde{n}^{\dagger}_{22} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
- \frac{c^{2}}{b^{2} - c^{2}}
\label{eq:n-tilde-dagger-22-triaxial}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{33} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
\frac{b^{2}}{b^{2} - c^{2}} \: ,
\label{eq:n-tilde-dagger-33-triaxial}
\end{equation}
where
\begin{equation}
F(\kappa, \phi) = 
\int^{\phi}_{0} 
\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
d\psi \: ,
\label{eq:F-kappa-phi}
\end{equation}
and
\begin{equation}
E(\kappa, \phi) = 
\int^{\phi}_{0} 
\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
d\psi \: ,
\label{eq:E-kappa-phi}
\end{equation}
with $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$ and
$\cos \phi = c/a$.
The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
called Legendre's normal elliptic integrals of the first and 
second kind, respectivelly. \citet{stoner1945} presented a 
detailed deduction of the demagnetizing factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
formulas.

@@

For prolate ellipsoids (e.g., $a > b = c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
- 1 \right\rbrace
\label{eq:n-tilde-dagger-11-prolate}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
\label{eq:n-tilde-dagger-22-prolate}
\end{equation}
where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
which uses the $\tilde{n}^{\dagger}_{11}$ defined in 
Eq. \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
The detailed deduction of the demagnetizing factors 
$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
can be found, for example, in \citet{stoner1945}. 
These formulas were posteriorly 
presented by \citet{emerson1985}.

@@

For oblate ellipsoids (e.g., $a < b = c$), the demagnetizing
factors obtained by solving Eq. \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = 
\frac{1}{1 - m^{2}} \left[
1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
\right] \: ,
\label{eq:n-tilde-dagger-11-oblate}
\end{equation}
where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
are calculated according to Eq.
\ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
defined in Equation \ref{eq:n-tilde-dagger-11-oblate}, 
and $m = a/b$.
The detailed deduction of these demagnetizing factors 
can be found, for example, in \citet{stoner1945}.
These formulas can also be found in \citet{emerson1985}.
The only difference, however, is that \citet{emerson1985} replaced
the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
the trigonometric identity 
$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.

@@

For triaxial ellipsoids (e.g., $a > b > c$), the functions
$g_{i}$ (Eq. \ref{eq:gi}) are defined as follows:
\begin{equation}
g_{1} = \frac{2}{\left( a^{2} - b^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:g1-triaxial}
\end{equation}
%\begin{equation}
%g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
%\left[ E\left(\kappa, \phi \right) 
%- \frac{\left( b^{2} - c^{2} \right)}{\left( a^{2} - c^{2} \right)}
%F\left(\kappa, \phi \right) 
%- \frac{\kappa^{2} \sin\phi \, \cos\phi}
%{\left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%\right]
%\label{eq:g2-triaxial}
%\end{equation}
\begin{equation}
g_{2} = \frac{2 \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
{\left( a^{2} - b^{2} \right)\left( b^{2} - c^{2} \right)}
\left\lbrace
E\left(\kappa, \phi \right) 
- \left( \frac{b^{2} - c^{2}}{a^{2} - c^{2}} \right)
F\left(\kappa, \phi \right) -
\frac{a^{2} - b^{2}}{\left( a^{2} - c^{2} \right)^{\frac{1}{2}}} \left[
\frac{c^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( b^{2} + \lambda \right)}
\right]^{\frac{1}{2}} \right\rbrace
\label{eq:g2-triaxial}
\end{equation}
and
%\begin{equation}
%g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
%\left[ \frac{\sin\phi \left( 1 - \kappa^{2} \sin^{2}\phi \right)^{\frac{1}{2}}}
%{\cos\phi}  - E\left(\kappa, \phi \right) \right]
%\: ,
%\label{eq:g3-triaxial}
%\end{equation}
\begin{equation}
g_{3} = \frac{2}{\left( b^{2} - c^{2} \right) \left( a^{2} - c^{2} \right)^{\frac{1}{2}}}
E\left(\kappa, \phi \right) +
\frac{2}{b^{2} - c^{2}}
\left[
\frac{b^{2} + \lambda}{\left( a^{2} + \lambda \right)\left( c^{2} + \lambda \right)}
\right]^{\frac{1}{2}}
\: ,
\label{eq:g3-triaxial}
\end{equation}
where $F(\kappa, \phi)$ and $E(\kappa, \phi)$ are defined by
Eqs. \ref{eq:E-kappa-phi} and \ref{eq:F-kappa-phi}, but with 
$\sin \phi = \sqrt{\left( a^{2} - c^{2} \right)/\left( a^{2} + \lambda \right)}$.
A deduction of these formulas was presented by \citet{tejedor1995}.
Despite the small differences, these formulas can also be found in
\citet{clark1986}.

@@

For prolate (e.g., $a > b = c$) ellipsoids, the functions
$g_{i}$ (Eq. \ref{eq:gi}) are given by:
\begin{equation}
g_{1} =  \frac{2}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right] -
\left( \frac{a^{2} - b^{2}}{a^{2} + \lambda} \right)^{\frac{1}{2}}
\right\rbrace
\label{eq:g1-prolate}
\end{equation}
and
\begin{equation}
g_{2} =  \frac{1}{\left( a^{2} - b^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\frac{\left[ \left( a^{2} - b^{2} \right)
             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
     {b^{2} + \lambda} -
\ln \left[ \frac{\left( a^{2} - b^{2} \right)^{\frac{1}{2}} + 
                 \left( a^{2} + \lambda \right)^{\frac{1}{2}}}{
                 \left( b^{2} + \lambda \right)^{\frac{1}{2}}} \right]
\right\rbrace \: ,
\label{eq:g2-prolate}
\end{equation}
where $g_{3} = g_{2}$.
These formulas can be obtained by properly manipulating those
presented by \citep{emerson1985}.

@@

For oblate (e.g., $a < b = c$) ellipsoids, the functions
$g_{i}$ (Eq. \ref{eq:gi}) are given by:
\begin{equation}
g_{1} =  \frac{2}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} -
\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right]
\right\rbrace
\label{eq:g1-oblate}
\end{equation}
and
\begin{equation}
g_{2} =  \frac{1}{\left( b^{2} - a^{2} \right)^{\frac{3}{2}}}
\left\lbrace
\tan^{-1} \left[ \left( \frac{b^{2} - a^{2}}{a^{2} + \lambda}\right)^{\frac{1}{2}} \right] -
\frac{\left[ \left( b^{2} - a^{2} \right)
             \left( a^{2} + \lambda \right) \right]^{\frac{1}{2}}}
     {b^{2} + \lambda}
\right\rbrace \: ,
\label{eq:g2-oblate}
\end{equation}
where $g_{3} = g_{2}$.
Similarly to the case of prolate ellipsoid shown previously,
these formulas can be obtained by properly manipulating those
presented by \citep{emerson1985}.
